### 2017-02-03 paper1.tex
Add files via upload

In this method, a "typical" longwave bandpass (approximately 4---42 \si{\micro\meter}) was extended to include much longer wavelengths. This was done for two reasons: 1. To accurately represent a longwave curve for typical urban T\textsubscript{surf}, which have significant emittance into wavelengths much longer than 42 \si{\micro\meter}. 2. To replicate the signal from a silicone-domed pyrgeometer, which is transmissive of radiation in wavelengths. A "typical" longwave bandpass underestimates a pyrgeometer signal by approximately 5---9 \si{\watt\per\square\meter}, depending on emitter temperature. Figure \ref{dometrans} comparison of ‘typical’ and ‘extended’ longwave bandpasses.

>>>>

In this method, a "typical" longwave bandpass, approximately 250 - 2215 \si{cm^{-1}} (4 - 42 \si{\micro\meter}), was extended to include much shorter wavenumber (longer wavelengths). This was done for two reasons: 1. To accurately represent a longwave curve for typical urban T\textsubscript{surf}, which have significant emittance into wavenumber shorter than 250 \si{cm^{-1}} (wavelengths much longer than 42 \si{\micro\meter}). 2. To replicate the signal from a silicone-domed pyrgeometer, which is transmissive of radiation in wavelengths. A "typical" longwave bandpass underestimates a pyrgeometer signal by approximately 5---9 \si{\watt\per\square\meter}, depending on emitter temperature. Figure \ref{dometrans} comparison of ‘typical’ and ‘extended’ longwave bandpasses.
